Draft

### 2016-10-06 Draft/draft.tex
Small fixes

\subsection{About \texorpdfstring{$e^{-i\pi S_y/\hbar}$}{}}
\label{sec:About-exp(-i*pi S_y/hbar)}

    (Related: Sakurai's Q.M., about (4.4.65)).

    Since 
    $$S_y=\frac{\hbar}{2}\sigma_y=\frac{\hbar}{2}
        \left( \begin{array}{cc}
         0 & -i \\
         i & 0 \\
        \end{array} \right)$$
    It is easy to check that $\sigma_y^2 = \mathbb{I}$. So:
    \begin{align*}
        e^{-i\phi S_y/\hbar}=
        e^{-i\frac{\phi}{2}\sigma_y}&=\sum_{n=0}^{\infty}
         \frac{(-i\frac{\phi}{2})^n(\sigma_y)^n}{n!}\nonumber\\
         &=\sum_{\text{odd }n}-\frac{i(\frac{\phi}{2})^n}{n!}\sigma_y
           + \sum_{\text{even }n}\frac{(i\frac{\phi}{2})^n}{n!}\mathbb{I}
    \end{align*}
    Using the taylor expansions:
    \begin{align}
        \sinh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n+1}}{(2n+1)!}
        \text{ (odd terms)}\\
        \cosh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n}}{(2n)!}
        \text{ (even terms)}
    \end{align}
    We see that:
    \begin{align}
        e^{-i\phi S_y/\hbar}=e^{-i\frac{\phi}{2}\sigma_y}&=
         - \sigma_y\sinh{i\frac{\phi}{2}}+ \mathbb{I}\cosh{i\frac{\phi}{2}}
         \nonumber\\
         &=
         -i\sigma_y \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
        \\
         &=-i\frac{2}{\hbar}S_y\sin{\frac{\phi}{2}}
            +\mathbb{I}\cos{\frac{\phi}{2}}
        \\
         &=\left( \begin{array}{cc}
            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
            \sin (\frac{\phi }{2}) & \cos (\frac{\phi }{2}) \\
         \end{array}\right)
    \end{align}
    So
    $$e^{-i\pi S_y/\hbar} = -i\frac{2S_y}{\hbar}$$
    By exactly the same argument, or simply by the symmetry
    ($x\leftrightarrow y$), we
    have:
    \begin{align}
        e^{-i\phi S_x/\hbar}=e^{-i\frac{\phi}{2}\sigma_x}&=
         -i\sigma_x \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
        \\
        &=-i\frac{2}{\hbar}S_x\sin{\frac{\phi}{2}}
            +\mathbb{I}\cos{\frac{\phi}{2}}
        \\
        &=\left(\begin{array}{cc}
            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
            \sin (\frac{\phi }{2}) & \cos(\frac{\phi }{2}) \\
         \end{array}\right)
    \end{align}
    Also, one can easily find that:
    \begin{align}
        e^{-i\phi S_z/\hbar}=e^{-i\frac{\phi}{2}\sigma_z}&=
          \left(\begin{array}{cc}
              e^{-i\frac{\phi }{2}} & 0 \\
              0                     & e^{i\frac{\phi }{2}} \\
         \end{array}\right)
    \end{align}
    Here a formula that encompass all the above relationship:
    \begin{align}
        \exp(\frac{-i\vec{\sigma}\cdot\hat{\vec{n}}\phi}{2})
        =
        \cos(\frac{\phi}{2})\mathbb{I}-i\vec\sigma\cdot\hat{\vec{n}}
        \sin(\frac{\phi}{2})
    \end{align}
    where $\vec\sigma=(\sigma_x,\sigma_y,\sigma_z)$, and 
    $\hat{\vec{n}}$ is any unit vector.
\section{Miscellnaneous Notes}
    \subsection{Super conductor}
    Mean-field approach to deal with a four operator diagonalization.

>>>>

\section{Miscellnaneous Notes}
    \subsection{Super conductor}
    Mean-field approach to deal with a four operator diagonalization.
